MaxEnt: What is it good for?

### 2015-06-21 ms.tex
few words in expectation section

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. An expected value is a property of a probability distribution,
and we can imagine updating from a prior $q$ to a posterior
$p$ when we receive information that specifies an expected value.
For example, suppose we apply the constraint (the testable information)
that the expected value of $f(x)$ should equal some known value $F$. That is:
\begin{eqnarray}
\left<f(x)\right>_p = \sum_x p(x)f(x) = F.
\end{eqnarray}

The resulting posterior distribution given by MaxEnt is:

\begin{eqnarray}
p(x) &=& \frac{1}{Z}q(x)\exp\left[-\lambda f(x)\right] 
\end{eqnarray}

>>>>

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. An expected value is a property of a probability distribution,
and we can imagine updating from a prior $q$ to a posterior
$p$ when we receive information that specifies an expected value.
For example, suppose we apply the constraint (the testable information)
that the expected value of $f(x)$ should equal some known value $F$. That is:
\begin{eqnarray}
\left<f(x)\right>_p = \sum_x p(x)f(x) = F.\label{eq:expected_value}
\end{eqnarray}

The resulting posterior distribution given by MaxEnt is:
\begin{eqnarray}
p(x) &=& \frac{1}{Z}q(x)\exp\left[-\lambda f(x)\right] 
\end{eqnarray}
That is, the posterior is proportional to the prior multiplied by a
``canonical'' factor. The value of $\lambda$ must be chosen so that
the constraint (Equation~\ref{eq:expected_value}) is satisfied. $Z$ is the
normalisation constant and implicitly depends on $\lambda$.

As an example, let's update the prior from Figure~\ref{fig:distribution}
using the testable information $\left<(x - 5)^2\right>_p = 1$.
